Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-25 main_paper.tex

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{\hat\tau(h) - \Delta^{*}(h,b) - \tau}{ V^{bc}(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9} and
$V^{bc}(h, b) = V(h) + C(h, b)$, both which are defined in Equations~\eqref{eq:8}
and~\eqref{eq:13} of the Mathematical Appendix.
\end{theorem}

Theorem~\ref{T1} implies that our bias-corrected
estimator has the same asymptotic distribution as CCT's. This equivalence should
be unsurprising; both estimators use a second order polynomial to directly estimate
the bias of the local linear model, so they should behave very similarly.

>>>>

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:18}
  \Delta^*(h,b) = h^{2} \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{equation}
almost surely and
\begin{equation}
  \label{eq:4}
  \frac{\hat\tau(h) - \Delta^{*}(h,b) - \tau}{ V^{bc}(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9} and
$V^{bc}(h, b) = V(h) + C(h, b)$, both which are defined in Equations~\eqref{eq:8}
and~\eqref{eq:13} of the Mathematical Appendix.
\end{theorem}

For practical purposes, Theorem~\ref{T1} implies that our bias-corrected
estimator has the same asymptotic distribution as CCT's. This equivalence should
be unsurprising; both estimators use a second order polynomial to directly estimate
the bias of the local linear model, so they should behave very similarly.
Equation~\eqref{eq:18} implies an even stronger relationship between the two
results, that the bias correction is equivalent to CCT's up to simulation error
in the bootstrap.
